\textls[-0]{\thetitle}

### 2023-04-01 frontmatters.tex
Fix Front matter
Fix front.
Fix.

% Title Page

\vspace*{\fill}
\begin{center}
  \textsc{\Huge \thetitle}
\end{center}

@@

@@

@@

>>>>

% Title Page
\pagenumbering{roman}
\vspace*{\fill}
\begin{center}
  \textsc{\Huge \thetitle}
\end{center}

@@

\setcounter{page}{1}

@@

This thesis consists of material all of which I authored or co-authored: see Statement of Contributions included in the thesis. This is a true copy of the thesis, including any required final revisions, as accepted by my examiners.

@@

Ende Jin and Prof. Yizhou Zhang co-authored Chapter 1.

Ende Jin is the sole author of Chapter 2, which were written under the  under the supervision of Prof. Yizhou Zhang.

Both Chapter 1 and Chapter 2 are already published result.

\noindentparagraph{Research presented in Chapter 1 and 2:} Ende Jin is the primary investigator of both theoretical development and practical implementation of the prototype. This work was supported in part by an Amazon research award on automated
reasoning.
